openarchaeoCollaboration

### 2023-06-14 analysis/openarchaeo_collaboration.qmd
Update usage instructions

```{r dependencies, include=FALSE}
library("fs")
library("geomtextpath")
library("ggiraph")
library("ggraph")
library("gt")
library("here")
library("khroma")
library("lubridate")
library("openarchaeoCollaboration")
library("patchwork")
library("tidygraph")
library("tidyverse")
```

>>>>

```{r dependencies, include=FALSE}
library("openarchaeoCollaboration") # this package, install with devtools::build()

library("fs")
library("geomtextpath")
library("ggiraph")
library("ggraph")
library("gt")
library("here")
library("khroma")
library("lubridate")
library("patchwork")
library("tidygraph")
library("tidyverse")
```
